Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
temp scale

To assess the influence of spatial scale, we aggregated the land cover raster at
varying scales relevant to caribou ecology. We aggregated the original 30 m land
cover raster using the R package `grainchanger` [@Graham_2019] across a series
of scales (100 - 1000 m by 100 m steps) The land cover raster was aggregated
using a modal moving window method using a circular window corresponding to the
above scales [@Graham_2019a]. We assume 30 m and 100 m represents fine-scale
decision making for caribou during foraging, while re-sampling at 500 m , 750 m
and 1000 m represents the scale at which caribou tend to select and avoid
habitat (Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
multilayer network consisting of the social association between `r DT[,
uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
forage) for the entire study period. We calculated graph strength and
multidegree for each habitat layer and spatial scale, and edge overlap across
the entire series of networks to determine proportion of total edges observed in
each combination of habitat layer and spatial scale.

### Temporal scale
We used a temporal multilayer network to assess seasonality of caribou social
associations. We generated layers

#### Time window length and position
We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for summer (starting at 3
August 2017) and winter (starting at 1 January 2018). The position of the time
window was shifted by 1-48 days, using a fixed time window length of 48 days.
These new time windows were iteratively used to partition data into two discrete
seasons (summer and winter) and generate multilayer networks.

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
fixed rate, e.g. every $x$ minutes or hours, continuously throughout the study
period. Fix rate is a reflection of number of observations an individual would
have been observed and recorded in traditional ethological studies.We
investigated the influence of the number of observations on resulting multilayer
networks. We randomly selected a maximum 485 timesteps for each season to
represent all possible observations. We regenerated multilayer networks and
calculated associations of individuals with 25 additional observations at each
iteration (10 - 485 observations). Subsequent iterations included the previous
set of observations to mimic collection of observational data.

>>>>

To assess the influence of spatial scale, we aggregated the land cover raster at
varying scales relevant to caribou ecology. We aggregated the original 30 m land
cover raster using the R package `grainchanger` [@Graham_2019] across a series
of scales (100 - 1000 m by 100 m steps) The land cover raster was aggregated
using a modal moving window method using a circular window corresponding to the
above scales [@Graham_2019a]. We assume 30 m and 100 m represents fine-scale
decision making for caribou during foraging, while re-sampling at 500 m , 750 m
and 1000 m represents the scale at which caribou tend to select and avoid
habitat (Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
multilayer network consisting of the social association between `r DT[,
uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
forage) for the entire study period. Social associations of individuals were
defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
strength and multidegree for each habitat layer and spatial scale, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial scale.

### Temporal scale
#### Time windows

We used a temporal multilayer network to assess the seasonality of caribou
sociality. Multilayer networks consisted of the social association between `r
DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
days from the entire study period. Social associations of individuals were
defined by spatiotemporal overlap within 5 minutes and 50 m. Within each time
window, we calculated individual's graph strength and multidegree. We calculated
edge overlap across the entire series of networks to determine proportion of
total edges observed in each time window.

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
fixed rate, e.g. every $x$ minutes or hours, continuously throughout the study
period. Fix rate is a reflection of number of observations an individual would
have been observed and recorded in traditional ethological studies. We
investigated the influence of the number of observations on resulting multilayer
networks. We randomly selected a maximum 485 timesteps for each season to
represent all possible observations. We regenerated multilayer networks and
calculated associations of individuals with 25 additional observations at each
iteration (10 - 485 observations). Subsequent iterations included the previous
set of observations to mimic collection of observational data.
